Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-14 paper/section_3_model.tex
Work on Multi-Head Attention section

The decoder is a function that estimates $p(y_t)$, the probability of the next
token, conditional on the past and the context embeddings $\bx_I$, $\bx_T$, and
$\bx_F$:
\begin{IEEEeqnarray*}{lCl}
   p(y_t) &=& \mathbb{P}(Y_t = y_t \mid \by_{<t}, \bx_I, \bx_T, \bx_F)
\end{IEEEeqnarray*}
In our architecture, the decoder consists of four layers of transformer blocks.
In each block, the conditioning on past tokens is computed using dynamic
convolutions \cite{Wu2018PayLA}, and the conditioning on the contexts is
computed using Scalar-Dot-Product attention \cite{Vaswani2017AttentionIA}.

\subsubsection{Scalar-Dot-Product Attention}

Let $\bh_t$ be the current hidden state. We first do a linear projection of
$\bh_t$ and the image embedding $\bx_I$ into a query, key, and value, so that
all three have the same dimension:
\begin{IEEEeqnarray*}{lCl}
   \bq_T &=& \bW_{Iq} \, \bh_t \\
   \bk_T &=& \bW_{Ik} \, \bx_I \\
   \bv_T &=& \bW_{Iv} \, \bx_I
\end{IEEEeqnarray*}
Then the attended image $\bx_I'$ is the weighted sum of the values, where the weights are
obtained from the dot product between the key and value:
\begin{IEEEeqnarray*}{lCl}
   \bx_I' &=& \text{softmax}\left( \bq \bk^T \right) \bv
\end{IEEEeqnarray*}
We use the same attention mechanism to obtain the attended article $\bx_T'$
and the attended face $\bx_F'$. These three are then concatenated and fed
through a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \bx_C' &=& [\bx_I', \bx_T', \bx_F'] \\
   \bx_O &=& \text{LayerNorm}(X_C + \bW_O \, \text{ReLU}(\bW_C \, \bx_C' + \bb_C) + \bb_O)
\end{IEEEeqnarray*}

For each generation step, we use the Scalar-Dot-Product attention
\cite{Vaswani2017AttentionIA} to attend to the image, article, and faces. All
of the three attended representations are then concatenated and fed as input to
the self-attention layer.

@@

Our decoder is a transformer architecture with dynamic convolutions
\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
found that using dynamic convolutions allows the training to converge faster
than using the current state-of-the-art GPT-2 architecture
\cite{Radford2019LanguageMA}.

In the standard self-attention module, the input embedding $\bx \in
\mathbb{R}^{1024}$ is first projected linearly into a query, key, and value
$\bm{q}, \bm{k}, \bm{v} \in \mathbb{R}^{1024}$.

>>>>

The decoder is a function that estimates $p(y_t)$, the probability of the next
token, conditional on the past $\by_{<t}$ and the context embeddings $\bX_I$,
$\bX_T$, and $\bX_F$:
\begin{IEEEeqnarray*}{lCl}
   p(y_t) &=& \mathbb{P}(Y_t = y_t \mid \by_{<t}, \bX_I, \bX_T, \bX_F)
\end{IEEEeqnarray*}
In our architecture, the decoder consists of four layers of transformer blocks.
In each block, the conditioning on past tokens is computed using dynamic
convolutions \cite{Wu2018PayLA}, and the conditioning on the contexts is
computed using multi-head attention \cite{Vaswani2017AttentionIA}.

\subsubsection{Multi-Head Attention}

Let $\bh_t \in \mathbb{R}^{1024}$ be the current hidden state when decoding the
$t$th token. We divide the embedding dimension into 16 attention heads, each
with size 64. For each head $i \in \{1, 2, ..., 16\}$, we first do a linear
projection of $\bh_t$ and the image embedding $\bX_I$ into a query $\bq_{It}
\in \mathbb{R}^{64}$, key $\bK_I \in \mathbb{R}^{64 \times 49}$, and value
$\bV_I \in \mathbb{R}^{64 \times 49}$:
\begin{IEEEeqnarray*}{lCl}
   \bq_{Iit} &=& \bW_{Iiq} \, \bh_t \\
   \bK_{Ii} &=& \bW_{Iik} \, \bX_I \\
   \bV_{Ii} &=& \bW_{Iiv} \, \bX_I
\end{IEEEeqnarray*}
Then the attended image for each head $\bx'_{Ii} \in \mathbb{R}^{64}$ is the
weighted sum of the values, where the weights are obtained from the dot product
between the query and key:
\begin{IEEEeqnarray*}{lCl}
   \bx'_{Ii} &=& \text{softmax}\left(\bK_{Ii}^T \bq_{Iit} \right) \bV_{Ii}
\end{IEEEeqnarray*}
The attention from each head is then concatenated into $\bx'_{I} \in
\mathbb{R}^{1024}$:
\begin{IEEEeqnarray*}{lCl}
   \bx'_{I} &=& [\tx_{I1}, \tx_{I2}, ..., \tx_{I16}]
\end{IEEEeqnarray*}
and the overall image attention $\tx_{I} \in \mathbb{R}^{1024}$ is obtained
after adding a residual connection and layer normalization:
\begin{IEEEeqnarray*}{lCl}
   \tx_{I} &=& \text{LayerNorm}(\bh_t + \bx'_{I})
\end{IEEEeqnarray*}
We use the same attention mechanism (with different weight matrices) to obtain
the attended article $\tx_T$ and the attended face $\tx_F$. These three are
then concatenated and fed through a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \tx_C &=& [\tx_I, \tx_T, \tx_F] \\
   \tx_R &=& \bW_C \, \tx_C + \bb_C \\
   \tx_D &=& \text{ReLU}(\bW_R \, \tx_R + \bb_R )\\
   \tx_E &=& \text{LayerNorm}(\tx_R + \bW_D \, \tx_D + \bb_D)
\end{IEEEeqnarray*}
The final output $\tx_E \in \mathbb{R}^{1024}$ is used as the input to the
next transformer block.

@@

Instead of using the standard self-attention module as in current
state-of-the-art GPT-2 architecture \cite{Radford2019LanguageMA}, we find that
dynamic convolutions \cite{Wu2018PayLA} are more efficient to train, especially
when there is limited GPU compute power.

Given an input $\bz_t \in \mathbb{R}^{1024}$, which can either be the input
embedding of the previous token, or the output from the previous transformer
block, we first use a feedforward layer with a gated linear unit (GLU)
\cite{Dauphin2017GLU} as the activation function:
\begin{IEEEeqnarray*}{lCl}
   \bz_t' &=& \text{GLU}(\bW_Z \, \bz_t + \bb_Z)
\end{IEEEeqnarray*}
